State of the Practice of Lattice Boltzmann Method Software Development

### 2021-05-17 StateOfPractice/Peter-Notes/Report/Report.tex
some notes on additions to Background section

this is about scs background

this is theoretical
-define SCS in more detail than introduction
- importance of qualities in SCS
- ensuring the quality can take time
-define software family (defined more/further in domain analysis)
-background of LBM and what they are used for, link to domain analysis section for further detail

" Scientific Computing (SC) is the subdomain of
computer science that uses computers to simulate and analyze continuous mathematical
models of physical systems. "
" As SmithEtAl2016 [8] shows, SC developers value documentation, but
they cannot see themselves meeting the required time constraints. Maintaining the doc-
umentation when some requirements change during development process makes the time
commitment even more difficult [2]. "
"The current approach to documentation
is largely a manual exercise, thus the quality is influenced by the author’s SC abilities. "

>>>>

this section is about scs background and software quality background, separate definitions of those and relationship between, also define software family

-define SCS in more detail than introduction
-uses computers to simulate and analyze continuous mathematical
models of physical system[add citation from prev paper]
- look at other related papers and cite
-look at other sources and cite

- importance of qualities in SCS
- add citations
- ensuring the quality can take time blurb
-" As SmithEtAl2016 [8] shows, SC developers value documentation, but
they cannot see themselves meeting the required time constraints. Maintaining the doc-
umentation when some requirements change during development process makes the time
commitment even more difficult [2]." paraphrase and cite
"The current approach to documentation
is largely a manual exercise, thus the quality is influenced by the author’s SC abilities. " paraphrase /cite
- add blurb about Drasil, like below
-define software family, add citation 
- examples?
